Automated Formal Synthesis of Safe Digital Controllers\\ for Continuous Plants

### 2018-05-10 automatica/paper.tex
section 8

Using the state-space models given in Section~\ref{exp:benchmarks}, 
our evaluation has the following two experimental goals:

@@

\item[EG2] \textbf{(sanity check)} Confirm the
stability and safety of the synthesized controllers outside of our model.

@@

We provide the results in Table~\ref{tab:results}.  Here 
\textit{Benchmark} is the name of the respective benchmark, 
\textit{Order} is the number of continuous variables, 
$\mathcal{F}_{\langle I_p,F_p \rangle}$ and $\mathcal{F}_{\langle p \rangle}$  
are the fixed- and floating-point precision used to model the plant, respectively;
while \textit{Time} is the total time required to synthesize a controller for the given
plant with one of the two methods.  Timeouts are indicated by~\xmark.  The
precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
chosen to be $I_c = 8$, $F_c = 8$ for fixed-point and 
$\mathcal{F}_{\langle p \rangle}$ is chosen to be half-precision for floating-point.

We split our evaluation into two sets of results: fixed- and floating-point. 
For the majority of the fixed-point benchmarks, we observe that the abstraction-based
back-end is faster than the basic multi-staged verification approach, and
finds one solution more (14) than the multi-staged back-end (13).  In direct
comparison, the abstraction-based approach is on average able to find a
solution in approximately 53\% of the time required using the multi-staged
back-end, and has a median run-time 0.5\,s, which is twenty times smaller
than the multi-staged approach.  The two back-ends complement each other in
benchmark coverage and together solve 58\% of the benchmarks.
%
For the majority of the floating-point benchmarks, we also observe that the abstraction-based
back-end is much faster than the basic multi-staged verification approach, but both
back-ends find the same amount of solutions (13).  In direct
comparison, the abstraction-based approach is on average able to find a
solution in approximately 50\% of the time required using the multi-staged
back-end, and has a median run-time 0.6\,s, which is forty times smaller
than the multi-staged approach.  The two back-ends complement each other in
benchmark coverage and together solve 54\% of the benchmarks.

>>>>

Using the state-space models described in Section~\ref{exp:benchmarks}, 
the evaluation study has the following two experimental goals:

@@

\item[EG2] \textbf{(Sanity check)} Confirm the
stability and safety of the synthesized controllers \note{[this is unclear, rephrase:]outside of our model.}

@@

We provide the results in Table~\ref{tab:results}, 
where \textit{Benchmark} is the name of the respective benchmark, 
\textit{Order} is the number of continuous variables of the model, 
$\mathcal{F}_{\langle I_p,F_p \rangle}$ and $\mathcal{F}_{\langle p \rangle}$  
are the fixed- and floating-point precisions used to model the plant, respectively,  
and \textit{Time} is the total time required to synthesize a controller for the given plant.    
Timeouts are indicated by~\xmark.  \note{ we should distinguish between timeouts and failures to synthesise. }
The precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
chosen to be $I_c = 8$, $F_c = 8$ for fixed-point, whereas  
$\mathcal{F}_{\langle p \rangle}$ is chosen to be half-precision for floating-point. \note{what about $\mathcal{F}_{\langle I_p,F_p \rangle}$?}

We separate our evaluation into two sets of results: fixed- and floating-point. 
For the majority of the fixed-point benchmarks, we observe that the abstraction-based
back-end is faster than the basic multi-staged verification approach, and
finds one solution more (14) than the multi-staged back-end (13).  In direct
comparison, the abstraction-based approach is on average able to find a
solution in approximately 53\% of the time required using the multi-staged
back-end, and has a median run-time 0.5\,s, which is twenty times smaller
than the multi-staged approach.  The two back-ends complement each other in
benchmark coverage and together solve 58\% of the benchmarks.
%
For the majority of the floating-point benchmarks, we also observe that the abstraction-based
back-end is much faster than the basic multi-staged verification approach, but both
back-ends find the same amount of solutions (13).  In direct
comparison, the abstraction-based approach is on average able to find a
solution in approximately 50\% of the time required using the multi-staged
back-end, and has a median run-time 0.6\,s, which is forty times smaller
than the multi-staged approach.  The two back-ends complement each other in
benchmark coverage and together solve 54\% of the benchmarks.
